---
title: "POC Code Trend Report"
output: html_document
---

```{r setup, include=FALSE}
#!/usr/bin/env Rscript
library(lubridate)
library(data.table)
library(dplyr)
library(zoo)

input_file <- "data/crs/test_crs.csv"
output_file <- "output.csv"
short_time <- 2
long_time <- 7
date_back <- "2017-01-01"

#command line argument parsing
args = commandArgs()

# test if there is at least one argument: if not, display a warning and use
# defaults
if (length(args)==0) {
  warning("default input output files will be used, and a 30 day and 1 year moving average for trending")
} else if (length(args)==5) {
  # default output file
  input_file <- args[1] 
  output_file <- args[2]
  short_time <- args[3]
  long_time <- args[4]
  date_back <- args[5]
  
}

knitr::opts_chunk$set(echo = TRUE)
commandArgs <- function(...)(c(input_file, output_file, short_time, long_time, date_back))
source('poc_code_date_trending_experiment.R')
print(codes_to_plot)
```

This report contains charts for the five best and worst POCs codes which `r short_time` moving average is trending the furthest from the `r long_time` simple moving average.  All numeric values are summations of probabilities and thus are unitless, and should be interpreted as relative to each other.

#POC Codes most decreasing in usage
```{r echo = FALSE}
getting_better_ <- abs(getting_better)
rownames(getting_better_)<-NULL
knitr::kable(getting_better_)
```

```{r echo=FALSE}
label <- " Day SMA"
for(i in colnames(getting_better)){
  #print(i)
  plot(x = date(poc_output_10.df$short_date), y = poc_output_10.df[[i]], type ='l', ylab = "Expected Value",xlab = "Date", main = i)
  lines(x = date(poc_output_200.df$short_date),y = poc_output_200.df[[i]], type ='l', col = 'red')
  legend(x = 'topright', legend=c(paste0(short_time,label),paste0(long_time, label)),
       col=c("black", "red"), lty=1)
}
```

#POC codes most increasing in usage
```{r echo = FALSE}
getting_worse_ <- getting_worse
rownames(getting_worse_)<-NULL
knitr::kable(getting_worse_)
```

```{r echo=FALSE}
for(i in colnames(getting_worse)){
  #print(i)
  plot(x = date(poc_output_10.df$short_date), y = poc_output_10.df[[i]], type ='l',ylab = "Expected Value",xlab = "Date",main = i)
  lines(x = date(poc_output_200.df$short_date),y = poc_output_200.df[[i]], type ='l', col = 'red')
  legend(x = 'topright', legend=c(paste0(short_time,label),paste0(long_time, label)),
       col=c("black", "red"), lty=1)
}
```
